Hyperbolic SMC: a Variational Proposal for Sequential Monte Carlo Phylogenetic Inference

### 2024-07-29 paper/paper.tex
Add title and authors

% ready for submission
\usepackage{neurips_2024}

@@

\title{Formatting Instructions For NeurIPS 2024}

@@

\author{%
  David S.~Hippocampus\thanks{Use footnote for providing further information
    about author (webpage, alternative address)---\emph{not} for acknowledging
    funding agencies.} \\
  Department of Computer Science\\
  Cranberry-Lemon University\\
  Pittsburgh, PA 15213 \\
  \texttt{hippo@cs.cranberry-lemon.edu} \\
  % examples of more authors
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \AND
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
}

>>>>

% ready for submission
\usepackage[preprint]{neurips_2024}

@@

\title{Hyperbolic SMC: a Variational Proposal for Sequential Monte Carlo Phylogenetic Inference}

@@

\author{%
  Alex Chen \\
  Department of Computer Science \\
  Columbia University \\
  \texttt{azc2110@columbia.edu} \\
  \And
  Antonio Khalil Moretti \\
  Department of Computer Science \\
  Columbia University \\
  \texttt{amoretti@cs.columbia.edu} \\
}
